---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ParametricAEM

<!-- badges: start -->
<!-- badges: end -->

The goal of ParametricAEM is to estimate a parametric age-reading error matrix based on data where multiple readers have read the same fish. The package contains four such example data sets in inst/extdata, and scripts for analysing each of these in the folder scripts. 

## Installation

You can install the development version of ParametricAEM from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("NorskRegnesentral/ParametricAEM")
```

## Example

```{r example}
library(ParametricAEM)
file_path = system.file("extdata",
                         "NSS_herring_scales.csv",
                          package = "ParametricAEM")
 data_nss_scales = read.csv(file_path, sep = ",")
 data_exp = data_nss_scales[data_nss_scales$expertise == 1, ] # Extract experts
 data_exp = data_exp[data_exp$age > 0, ]
 data_analysis = Compute_modes(data_exp)
 data_analysis_capped = Cap_ages(data_analysis)
 fit = Estimate_model(data = data_analysis_capped,
                      min_age = 3,
                      max_age = 12,
                      start = c(2, 0, 0, 0, 0.2),
                      estimate = c(1, 1, 1, 1, 1))
 errormatrix = Calculate_matrix(fit$estimate[, "Estimate"], min_age = 3, max_age = 12)
 round(errormatrix, 3)

## basic example code
```

