---
title: "Data examples"
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Data examples
The four data sets are examples of age-reading exchange data sets where individual fish are aged by several readers. Mackerel_otoliths.csv contains otolith readings of Atlantic mackerel, NSAS_herring_otoliths.csv contains otolith readings of North Sea Autumn-Spawning herring, NSS_herring_otoliths.csv contains otolith readings of Norwegian Spring-Spawning herring, and NSS_herring_scales.csv contains scale readings of Norwegian Spring-Spawning herring. 

# Columns used in ParametricAEM
In this R-package, we use the following columns
*FishID: String, individual identifier for each fish
*reader: String, identifier for each individual reader
*expertise: Boolean, indicator for whether the reader is an expert (1) or not (0)
*age: Integer, age read by the reader

An extract of the relevant columns for the scale readings of Norwegian Spring-Spawning herring is shown below

```{r}

file_path = system.file("extdata",
                         "NSS_herring_scales.csv",
                          package = "ParametricAEM")
data_nss_scales = read.csv(file_path, sep = ",")
data_sub = data_nss_scales[,c("FishID", "reader", "expertise", "age")]
head(data_sub, n = 50)
```
